Geometric variational problems

### 2020-11-16 NSF2020/Description/background.tex
tidied it up; removed hyperlinks + pagination

To establish an attraction between interfaces, the water activity is not
arbitrary but rather is the solution of the screened Laplace
equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0, \mbox{ } \mathbf{x} \in \Omega, \qquad
  u = f,  \mbox{ } \mathbf{x} \in \partial \Omega, \qquad 
  u(\mathbf{x}) \to 0, \mbox{ as } |\mathbf{x}| \to \infty.
\end{equation}
The boundary values $f$ define the degree of hydrophobicity of the
water-particle interface: $f=1$ describes a hydrophobic interface, and
$f=0$ describes a hydrophilic interface. Thus, $f$ encodes information
about the particles, and the parameters $\rho$ and $\gamma$ encode
information about the quality of the solvent~\cite{Israelachvili1954,
Discher2002}. In practice, we integrate~\eqref{HAP} by parts and
use~\eqref{SL} to obtain
\begin{equation}
\label{eq:HAP_easy}
\Phi = -\gamma \int_{\partial \Omega} \rho u \nabla u \cdot \boldsymbol{\nu} \,\dif S,
\end{equation}
thereby avoiding volume integral calculations.

@@

The HAP formulation is, to our knowledge, the first demonstration of
bilayer self-assembly by a continuum-based interaction
model~\cite{Noguchi2001, Farago2003, Brannigan2006, Brooks2009,
Wang2013}. Our simulations use Janus particles to model lipid
amphiphiles which are popular in material science and physics for
creating functional materials~\cite{Lee2014, Lee2013}. Janus particles
are typically spherical with a biphasic material label on either
hemisphere, endowing the particle with a directional order. We model an
elongated lipid by elliptical particles with the hydrophobic label
defined along the ellipse's axis. 
\begin{wrapfigure}[14]{l}{0.35\textwidth}
\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:demixing} \footnotesize An initial assembly of
  small and large particles spontaneously segregates into two smaller
  bodies.}
\end{wrapfigure}
Under the hydrophobic force, with
excluded volume, the Janus particles spontaneously merge and realign
to form bilayers. This occurs only as a result of energy minimization
and does not require artificial inputs.
%

%
It is worth emphasizing that the HAP model uses only a few parameters:
interfacial tension, decay length, repulsion strength, and particle
shape. For example, an elastic modulus for stretching a vesicle from
micropipette manipulation directly calibrates our interfacial tension
parameter. This is in direct contrast with pair-potential-based
approaches in MD simulations and coarse-grained models where many more
parameters are required~\cite{Varilly2011, Wang2013}.
%MD simulators have also made measurements and lately there is better and better agreement with reality. 
%But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .

>>>>

To establish an attraction between interfaces, the water activity is not
arbitrary but rather is the solution of the screened Laplace
equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0, \mbox{ } \mathbf{x} \in \Omega, \qquad
  u = f,  \mbox{ } \mathbf{x} \in \partial \Omega, \qquad 
  u(\mathbf{x}) \to 0, \mbox{ as } |\mathbf{x}| \to \infty.
\end{equation}
The boundary values $f$ define the degree of hydrophobicity of the
water-particle interface: $f=1$ describes a hydrophobic interface, and
$f=0$ describes a hydrophilic interface. Thus, $f$ encodes information
about the particles, and the parameters $\rho$ and $\gamma$ encode
information about the quality of the solvent~\cite{Israelachvili1954,
Discher2002}.
In the figures throughout the proposal, red is for $u = 1$ and blue is for $u = 0$.
In practice, we integrate~\eqref{HAP} by parts and
use~\eqref{SL} to obtain
\begin{equation}
\label{eq:HAP_easy}
\Phi = -\gamma \int_{\partial \Omega} \rho u \nabla u \cdot \boldsymbol{\nu} \,\dif S,
\end{equation}
thereby avoiding volume integral calculations.

@@

\begin{wrapfigure}[14]{l}{0.35\textwidth}
\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:demixing} \footnotesize An initial assembly of
  small and large particles spontaneously segregates into two smaller
  bodies.}
\end{wrapfigure}
The HAP formulation is, to our knowledge, the first demonstration of
bilayer self-assembly by a continuum-based interaction
model~\cite{Noguchi2001, Farago2003, Brannigan2006, Brooks2009,
Wang2013}. Our simulations use Janus particles to model lipid
amphiphiles which are popular in material science and physics for
creating functional materials~\cite{Lee2014, Lee2013}. Janus particles
are typically spherical with a biphasic material label on either
hemisphere, endowing the particle with
a directional order. We model an
elongated lipid by elliptical particles with the hydrophobic label
defined along the ellipse's axis. 
Under the hydrophobic force, with
excluded volume, the Janus particles spontaneously merge and realign
to form bilayers. This occurs only as a result of energy minimization
and does not require artificial inputs.
%

%
It is worth emphasizing that the HAP model uses only a few parameters:
interfacial tension, decay length, repulsion strength, and particle
shape. For example, an elastic modulus for stretching a vesicle from
micropipette manipulation calibrates our interfacial tension
parameter. This is in direct contrast with pair-potential-based
approaches in MD simulations and coarse-grained models where many more
parameters are required~\cite{Varilly2011, Wang2013}.
%MD simulators have also made measurements and lately there is better and better agreement with reality. 
%But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .

### 2020-11-16 NSF2020/Description/preliminarywork.tex
tidied it up; removed hyperlinks + pagination

\vspace{-0.1cm}
\begin{wraptable}[8]{r}{0.53\textwidth}
\vspace{-0.1cm}
\centering{
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP                     & experiment          & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
}
  \vspace{-8pt}
\caption{\label{tab:moduli} \footnotesize Comparison of values of elastic
  moduli from the experimental literature and derived by HAP
  simulation.} 
\end{wraptable}
\section{Preliminary work}
\label{sec:preliminary_work}
PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
%
%
%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
%PhD student and is currently a postdoc with PI RR. The collaboration
%involved theoretical work and simulation. The theoretical work included
%model development, proving the first variation formula~\eqref{stress}
%and force-free law, and an energy-based uniqueness theorem for the
%exterior domain problem~\eqref{SL}. 
%Coauthors Andreas Kl\"ockner
%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
%simulations on NJIT clusters.
%
%\begin{wraptable}[11]{l}{0.43\textwidth}
%\centering{
%  \begin{tabular}{|l|l|l|l|}
%    $n$   & (rel.~err.)$_F$
%    &  (rel.~err.)$_G$ \\
%    \hline
%% 32   &   4.07466     &   1.56437\\
%% 64   &   0.24664     &   0.03476\\
%% 128  &   0.00063     &   0.00006\\
%  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
%  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
%  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
%  \end{tabular}}
%\vspace{-5pt}
%\caption{\label{tab:spectral_force} 
%\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
%  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
%  and (rel.~err.)$_G = \max_{i}
%  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
%  for force and torque respectively as a function of number of grid
%  points $n$ per particle.  The data is for $N = 5$ particles; two of
%  the particles are nearly touching at a distance 1\% of particle
%  diameter.} 
%\end{wraptable}
The results are summarized in \cite{Fu2018_SIAM}, where
small particle-number simulations successfully demonstrated gradient-driven self-assembly of
amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
the model parameters: decay length $\rho=2.5$ nm (based on measurements of
hydrophobic attraction between surfactant-coated
membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
particle diameter $\delta = 2.0$ nm (the physical monolayer thickness~\cite{Boal}),
and interfacial tension $\gamma = 4$ pN nm$^{-1}$ (based on
measurements for single-component bilayer lipid
membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}).

%\begin{wrapfigure}[]{r}{0.5\textwidth}
%  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
%  \vspace{-25pt}
%  \caption{\label{fig:tank_treading} \footnotesize
%    Panel A shows water activity and flow direction for  a two-dimensional
%    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
%    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
%    mean angular velocities for the outer leaflet and the inner
%    respectively.  Panel C shows that the trajectory of the particle
%    centers forms two ellipses with well-defined inclination angle
%    $\Theta$. Panel D shows the evolution of the inclination angle.
%    Panels B and D share the same time axis.}
%\end{wrapfigure}
The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
loading a partially clamped planar bilayer. The second used a harmonic
bond to dilate a circular bilayer. The third measured tilt using a decay
equation from~\cite{KUZMIN2005}. These simulations isolated three of the
five deformations of~\eqref{ansatz3}, enabling us to read off elastic
moduli from simulation data. The results agreed remarkably well with the
values reported in the experimental literature (Table~\ref{tab:moduli}).
The agreement is underscored by the fact that the two main HAP
parameters, $\gamma$ and $\rho$, were assigned physical values from the
outset rather than being tuned to fit data.

\begin{wraptable}[11]{l}{0.43\textwidth}
\centering{
  \begin{tabular}{|l|l|l|l|}
    $n$   & (rel.~err.)$_F$
    &  (rel.~err.)$_G$ \\
    \hline
% 32   &   4.07466     &   1.56437\\
% 64   &   0.24664     &   0.03476\\
% 128  &   0.00063     &   0.00006\\
  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
  \end{tabular}}
\vspace{-5pt}
\caption{\label{tab:spectral_force} 
\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
  and (rel.~err.)$_G = \max_{i}
  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
  for force and torque, respectively, as a function of number of grid
  points $n$ per particle. The data is for $N = 5$ particles; two of
  the particles are nearly touching at a distance 1\% of particle
  diameter.} 
\end{wraptable}
PIs BQ, RR, and YNY initiated a collaboration in Summer 2020 to
develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
date, we have written solvers for the two-dimensional boundary integral
formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
third-order accuracy up to the boundary. The specialized reciprocal
identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
torque (Table~\ref{tab:spectral_force}).

\begin{wrapfigure}[]{r}{0.5\textwidth}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional,
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. The color coding is for HAP. Panel B: The
    mean angular velocities for the outer and the inner leaflets, 
    respectively. Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}

We have simulated two-dimensional vesicles in shear flow
$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
$\dot{\gamma}$,
%(The symbol shear rate is unrelated to interfacial tension.)
and the particle-based system mimics the behavior observed in continuous
vesicles~\cite{torres-sanchez_millan_arroyo_2019,
mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
pattern is that of a vesicle bilayer approaching a steady, tank-treading
ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
data in the context of theoretical work on
tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
a tank-treading frequency as the mean, particle angular
velocities. The measured steady-state frequencies were within 7\% of the predicted 
frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
The inclincation angle of the particle-based simulation also
follows the inclination angle $\Theta$ predicted by Jeffrey's
equation (Figure~\ref{fig:tank_treading}D), albeit with some higher frequency oscillation
coming from particle reorganization.

Analyzing for any underlying constitutive laws, the particles reorganize
so that there is an initial increase and then plateau in vesicle
circumference. As is the case with real lipid bilayer membranes, the
particle collection permits a small amount of stretching. The
theoretical calculations give an increase of length by 3.6\%, and this amount
agrees with our measured increase in length. The simulations also
suggest that the particle system behaves as a semipermeable
vesicle~\cite{323e9a2f0c58487ea82518d7a1f96485, YAO2017728}.

\begin{wrapfigure}[11]{l}{0.22\textwidth}
  \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
  \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
  two-dimensional vesicle at large shear rates.}
\end{wrapfigure}
The above considerations further justify using the particle-based model
to study material properties as outlined in
\S\ref{subsec:specific_aim_1}. Furthermore, the particle system allows
for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}. In
Figure \ref{fig:tank_treading}B, the inner angular velocity is slightly
less than the outer angular velocity. Intermonolayer slip enters
zero-thickness membrane models as a velocity jump boundary condition
\cite{schwalbe_vlahovska_miksis_2010}, for example, but in the present
model, it is a consequence of monolayer independence. For large shear
rates, viscous forces exceed the hydrophobic attraction to the point that
the vesicle ruptures, and the flow carries away segmented membrane patches
(Figure \ref{fig:flow_rupture}).

>>>>

\vspace{-0.1cm}
\begin{wraptable}[8]{r}{0.55\textwidth}
\vspace{-0.1cm}
\centering{
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP                     & experiment          & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
}
  \vspace{-8pt}
\caption{\label{tab:moduli} \footnotesize Comparison of values of elastic
  moduli from the experimental literature and derived by HAP
  simulation.} 
\end{wraptable}
\section{Preliminary work}
\label{sec:preliminary_work}
PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
%
%
%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
%PhD student and is currently a postdoc with PI RR. The collaboration
%involved theoretical work and simulation. The theoretical work included
%model development, proving the first variation formula~\eqref{stress}
%and force-free law, and an energy-based uniqueness theorem for the
%exterior domain problem~\eqref{SL}. 
%Coauthors Andreas Kl\"ockner
%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
%simulations on NJIT clusters.
%
%\begin{wraptable}[11]{l}{0.43\textwidth}
%\centering{
%  \begin{tabular}{|l|l|l|l|}
%    $n$   & (rel.~err.)$_F$
%    &  (rel.~err.)$_G$ \\
%    \hline
%% 32   &   4.07466     &   1.56437\\
%% 64   &   0.24664     &   0.03476\\
%% 128  &   0.00063     &   0.00006\\
%  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
%  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
%  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
%  \end{tabular}}
%\vspace{-5pt}
%\caption{\label{tab:spectral_force} 
%\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
%  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
%  and (rel.~err.)$_G = \max_{i}
%  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
%  for force and torque respectively as a function of number of grid
%  points $n$ per particle.  The data is for $N = 5$ particles; two of
%  the particles are nearly touching at a distance 1\% of particle
%  diameter.} 
%\end{wraptable}
The results are summarized in \cite{Fu2018_SIAM}, where
small particle-number simulations successfully demonstrated gradient-driven self-assembly of
amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
the model parameters: decay length $\rho=2.5$ nm (based on measurements of
hydrophobic attraction between surfactant-coated
surfaces~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
particle diameter $\delta = 2.0$ nm (the physical monolayer thickness~\cite{Boal}),
and interfacial tension $\gamma = 4$ pN nm$^{-1}$ (based on
measurements for single-component bilayer lipid
membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}).

%\begin{wrapfigure}[]{r}{0.5\textwidth}
%  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
%  \vspace{-25pt}
%  \caption{\label{fig:tank_treading} \footnotesize
%    Panel A shows water activity and flow direction for  a two-dimensional
%    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
%    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
%    mean angular velocities for the outer leaflet and the inner
%    respectively.  Panel C shows that the trajectory of the particle
%    centers forms two ellipses with well-defined inclination angle
%    $\Theta$. Panel D shows the evolution of the inclination angle.
%    Panels B and D share the same time axis.}
%\end{wrapfigure}
\begin{wraptable}[10]{l}{0.43\textwidth}
\centering{
  \begin{tabular}{|l|l|l|l|}
    $n$   & (rel.~err.)$_F$
    &  (rel.~err.)$_G$ \\
    \hline
% 32   &   4.07466     &   1.56437\\
% 64   &   0.24664     &   0.03476\\
% 128  &   0.00063     &   0.00006\\
  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
  \end{tabular}}
\vspace{-5pt}
\caption{\label{tab:spectral_force} 
\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
  and (rel.~err.)$_G = \max_{i}
  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
  for force and torque, respectively, as a function of number of grid
  points $n$ per particle. The data is for $N = 5$ particles; two of
  the particles are nearly touching at a distance 1\% of particle
  diameter.} 
\end{wraptable}
The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
loading a partially clamped planar bilayer. The second used a harmonic
bond to dilate a circular bilayer. The third measured tilt using a decay
equation from~\cite{KUZMIN2005}. These simulations isolated three of the
five deformations of~\eqref{ansatz3}, enabling us to read off elastic
moduli from simulation data. The results agreed remarkably well with the
values reported in the experimental literature (Table~\ref{tab:moduli}).
The agreement is underscored by the fact that the two main HAP
parameters, $\gamma$ and $\rho$, were assigned physical values from the
outset rather than being tuned to fit data.

PIs BQ, RR, and YNY initiated a collaboration in summer 2020 to
develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
date, we have written solvers for the two-dimensional boundary integral
formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
third-order accuracy up to the boundary. The specialized reciprocal
identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
torque (Table~\ref{tab:spectral_force}).

\begin{wrapfigure}[22]{r}{0.5\textwidth}
\vspace{-5pt}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional, 
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. (Compare with \cite{Brandner2019}).
    Panel B: Angular velocities for the outer and the inner leaflets.
    Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}
We have simulated two-dimensional vesicles in shear flow
$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
$\dot{\gamma}$,
%(The symbol shear rate is unrelated to interfacial tension.)
and the particle-based system mimics the behavior observed in continuous
vesicles~\cite{torres-sanchez_millan_arroyo_2019,
mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
pattern is that of a vesicle bilayer approaching a steady, tank-treading
ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
data in the context of theoretical work on
tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
a tank-treading frequency as the mean of the particle angular
velocities. The measured steady-state freque ncies were within 7\% of the predicted 
frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
The inclincation angle of the particle-based simulation also
follows the inclination angle $\Theta$ predicted by Jeffrey's
equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation
coming from particle reorganization.

Analyzing for any underlying constitutive laws, the particles reorganize
so that there is an initial increase and then plateau in vesicle
circumference. As is the case with real lipid bilayer membranes, the
particle collection permits a small amount of stretching. The
theoretical calculations give an increase of length by 3.6\%, in
agreement with our measured length increase. The simulations also
suggest that the particle system behaves as a semipermeable
vesicle~\cite{323e9a2f0c58487ea82518d7a1f96485, YAO2017728}.

\begin{wrapfigure}[10]{l}{0.22\textwidth}
% \vspace{-5pt}
  \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
 \vspace{-20pt}
  \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
  two-dimensional vesicle at large shear rates.}
\end{wrapfigure}
The above considerations further justify using the particle-based model
to study material properties as outlined in
\S\ref{subsec:specific_aim_1}. Furthermore, the particle system allows
for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}. In
Figure \ref{fig:tank_treading}B, the inner angular velocity is slightly
less than the outer angular velocity. Intermonolayer slip enters
zero-thickness membrane models as a velocity jump boundary condition
\cite{schwalbe_vlahovska_miksis_2010}, for example, but in the present
model, it is a consequence of monolayer independence. For large shear
rates, viscous forces exceed the hydrophobic attraction leading to
 vesicle rupture~\cite{C8SM01501E}, at which point the flow carries away segmented membrane patches
(Figure \ref{fig:flow_rupture}).
